### 2016-03-09 paper.tex
initial files

\documentclass{easychair}
\usepackage{microtype}

\title{Specifying corporate BYOD policies with authorization logic}
\author{
  Joseph Hallett\inst{1}
  \and
  David Aspinall\inst{1}
}

\institute{
  University of Edinburgh
}

\begin{document}
\maketitle

Hello world

\end{document}

### 2016-03-09 paper.tex
outline
UNFINISHED: upto three pages

@@
 
-\title{Specifying corporate BYOD policies with authorization logic}
+\title{Specifying BYOD Policies With Logics Of Authorization}
+\titlerunning{Specifying BYOD Policies With Logics Of Authorization}
 \author{
@@
 }
+\authorrunning{Hallett and Aspinall}
 
@@
 
+% AppPAL and Listing formatting
+\lstdefinelanguage{AppPAL}{%
+  morekeywords={if,inf,says,where,true,false},
+  otherkeywords={can-act-as,can-say},
+  sensitive=true,
+  morestring=[b]',
+  literate={\ inf\ }{{$\infty$}}5
+}[keywords,strings]
+\lstset{%
+  basicstyle=\ttfamily\footnotesize{},
+  stringstyle=\sffamily\footnotesize{},
+  keywordstyle=\ttfamily\slshape\footnotesize{},
+  language=AppPAL,
+  columns=flexible,
+  frame=single
+}
+
 \begin{document}
@@
 
-Hello world
+\begin{abstract}
+  % State problem
+  % Why is it interesting
+  % What does my solution achieve
+  % What follows from solution
+\end{abstract}
 
+\section{Introduction}
+% Corporate policies are poorly specified
+% We have used an authorization to specify them and this is interesting
+
+Employees are increasingly bringing their own devices into their workplaces (called \emph{bring your own device} or BYOD schemes).
+This can present a challenge for corporate IT departments:
+  they need to secure their networks and data but as they do not provide the employees with the devices they have limited control over what software runs and how the devices are configured.
+As a means of controlling the devices, IT departments have taken to publishing mobile device policies.
+Employees must agree to follow these policies if they want to use their personal devices in work.
+Often these policies are specified using natural language.
+This is problematic as it can create ambiguity in how the policy should be enforced, and in how the IT department can confirm that the policy was followed.
+There may be issues with \emph{completeness} and \emph{consistency} in these policies, which can lead to problems in enforcement.
+
+Logics of authorization are languages designed to express rules about permissible actions.
+\emph{AppPAL}~\cite{Hallett:2016vu} is a language designed to express policies about which mobile apps to use and install.
+AppPAL is an instantiation of Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} and can express complex delegation relationships as well as make use of external programs and constraints such as static analysis tools, whilst being decidable and having formal semantics.
+We believe AppPAL can also be used to help specify BYOD policies. 
+We present in Section~\ref{sec:translation} excerpts from the translation into AppPAL of three BYOD policies: one from a security policy template from the SANS institute to aid companies in developing their own policies~\cite{Guerin:2008we}, another from an NHS hospital trust describing what their doctors may do with their phones and their role in the treatment of patients~\cite{Kennington:2014tr}, finally a simplistic policy used in practice from the University of Edinburgh~\cite{Williamson:2015tr}.
+
+% TODO: We found that...
+
+\section{Translating Corporate Policies}
+\label{sec:translation}
+
+It is common to find rules in policies describing what apps can be used on devices.
+This is modeled in AppPAL through the \texttt{isInstallable} predicate.
+The Edinburgh policy only recommends that apps come from a reputable source though what it means to be \emph{reputable} is left undefined. 
+\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Only download applications (‘apps’) or other software from reputable sources.''}]
+'edinburgh-policy' says Store can-say App isInstallable if Store sells(App), Store isReputable.
+\end{lstlisting}
+Whereas the SANS policy require the IT department maintain white and black lists of acceptable apps:
+\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorzed applications and makes them available to users on the intranet.''}]
+'sans-policy' says 'it-department' can-say App isInstallable.
+\end{lstlisting}
+This rule is replicated later in the policy by another recommendation that says the same:
+\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Only approved third party applications can be
+installed on handhelds. The approved list can be
+obtained by contacting the IT department, or should be
+available on the intranet.''}]
+'sans-policy' says 'it-department' can-say App isInstallable.
+\end{lstlisting}
+The NHS policy makes a distinction between \emph{clinical} and \emph{non-clinical} apps with each requiring approval through a different group before final approval is given by the \emph{Integrated Governance Committee}.
+These rules are only theoretical however as no group has ever approved an app.
+\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
+Apps for work usage must not be downloaded onto corporately issued mobile devices (even if approved on the NHS apps store) unless they have been approved through the following Trust channels: Clinical apps; at the time of writing there are no apps clinically approved by the Trust for use with patients / clients.
+However, if a member of staff believes that there are clinical apps or other technologies that could benefit their patients / clients, this should be discussed with the clinical lead in the first instance and ratification should be sought via the Care and Clinical Policies Group.
+A clinical app should not be used if it has not been approved via this group.
+Business apps; at the time of writing there are no business (i.e., non-clinical) apps approved by the Trust for use other than those preloaded onto the device at the point of issue.
+However, if a member of staff believes that there are apps or other technologies that could benefit their non-clinical work, ratification of the app must be sought via the Management of Information Group (MIG).
+An app should not be used if it has not been approved via this group.
+Following approval through Care and Clinical Policies and / or MIG, final approval will be required through Integrated Governance Committee.''}]
+'nhs-policy' says App isInstallable if App isUsable, App isFinallyApproved.
+'nhs-policy' says 'cacpg' can-say App isUsable if App isUsableClinically.
+'nhs-policy' says 'mig' can-say App isUsable if App isUsableNonClinically.
+'nhs-policy' says 'igc' can-say App isFinallyApproved.
+\end{lstlisting}
+
+In each case the rules for deciding whether an employee could install an app took the form of a delegation to one or more third-parties to approve apps.
+By translating the policies into AppPAL problems become immediately apparent: the Edinburgh policy is incomplete as there was no way to determine what stores were reputable, the SANS policy contains duplicated rules, and the NHS policy is redundant as no app had ever been approved for use.
+In each case the AppPAL rule was no longer than the natural language policy, and in the case of the NHS policy considerably shorter and clearer.
+
+Some rules also appear to be common between different policies.
+For example both the NHS and SANS policies contain rules on the use of mobile devices in cars.
+The NHS policy requires employees do not use devices in cars, and recommends against using them even with hands-free equipment:
+\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
+For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
+It is illegal to do so.
+Please refer to the most up-to-date information via the Highways Agency.
+For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
+It is illegal to do so.
+Please refer to the most up-to-date information via the Highways Agency.''}]
+'nhs-policy' says Device mustNotOperate 
+  if Device isOwnedBy(Owner)
+  where inCar(Device) = true, isDriving(Owner) = true.
+\end{lstlisting}
+Whereas the SANS policy requires the use of hands-free devices when in a car.
+\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Conducting telephone calls or utilizing handhelds while driving can be a safety hazard.
+Drivers should use handhelds in hand only while parked or out of the vehicle.
+If employees must use a handheld device while driving, ⟨Company⟩ requires the use of hands-free headset devices.''}]
+'sans-policy' says Device mustNotOperate 
+  if Device isOwnedBy(Owner)
+  where inCar(Device) = true, isDriving(Owner) = true, isUsingHandsFree(Device) = false.
+\end{lstlisting}
+The similarity between the two rules is immediately apparent when specified in AppPAL: the SANS version has an additional constraint but they are otherwise identical.
+Other similarities appear when looking at how devices connect to networks.  The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks:
+\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks''}]
+'edinburgh-policy' says Device canConnectTo(AP) if AP isSecure.
+\end{lstlisting}
+
+Similarities between policies suggest that one could define a common schema of BYOD predicates, which would allow different policies to be compared and contrasted \emph{precisely} using standard terms.
+
+\section{Conclusions}
+% Related work:
+%   Existing systems for enforcement (mobile iron)
+%   Other work translating policies into formal language
+% Future work:
+%   Full case study translating and implementing a policy into AppPAL
+% Conclusion:
+%   Natural language policies don't work
+%   Formal specification helpful.
+
+\bibliographystyle{plain}
+\bibliography{paper}
 \end{document}

### 2016-03-09 paper.tex
UNFINISHED: moved bibtex inline since it is so short and made space

@@
 
-\title{Specifying BYOD Policies With Logics Of Authorization}
-\titlerunning{Specifying BYOD Policies With Logics Of Authorization}
+\title{Specifying BYOD Policies with Authorization Logic}
+\titlerunning{Specifying BYOD Policies with Authorization Logic}
 \author{
@@
 
+\newcommand{\dotdotdot}[1]{$\[\cdots\]$}
+
 \begin{document}
@@
   % State problem
+  Corporate BYOD policies are imprecisely specified using natural language.
   % Why is it interesting
+  This creates ambiguity and makes detecting issues, and comparing policies harder.
   % What does my solution achieve
+  We show how AppPAL (an authorization logic for mobile app installation policies) can describe BYOD policies formally.
   % What follows from solution
+  This suggests that BYOD policies can be enforced automatically, and with greater precision, than by relying on users.
 \end{abstract}
@@
 
-Employees are increasingly bringing their own devices into their workplaces (called \emph{bring your own device} or BYOD schemes).
+Employees are increasingly bringing their own devices into their workplaces.
 This can present a challenge for corporate IT departments:
@@
 
-\section{Translating Corporate Policies}
+\section{Translating Corporate BYOD Policies}
 \label{sec:translation}
@@
 The similarity between the two rules is immediately apparent when specified in AppPAL: the SANS version has an additional constraint but they are otherwise identical.
-Other similarities appear when looking at how devices connect to networks.  The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks:
-\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks''}]
+Other similarities appear when looking at how devices connect to networks.
+The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks, where as SANS says its okay if the access point is secured properly or a VPN is used:
+\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
 'edinburgh-policy' says Device canConnectTo(AP) if AP isSecure.
 \end{lstlisting}
-
-Similarities between policies suggest that one could define a common schema of BYOD predicates, which would allow different policies to be compared and contrasted \emph{precisely} using standard terms.
+\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``If mobile workers do require connectivity through public, open, or untrusted WLAN, then users MUST use WLANs using, if available and in this order: WPA(2) encryption, WEP 256 bits (or 128 bits), or finally open networks if nothing else is available.
+Users connected to data networks in an open environment MUST use a VPN connection.''}]
+'sans-policy' says Device canConnectTo(AP) if AP isSecure.
+'sans-policy' says AP isSecure if AP canUseWPA2.
+'sans-policy' says AP isSecure if AP canUseWEP256.
+'sans-policy' says AP isSecure if AP canUseWEP128.
+'sans-policy' says Device canConnectTo(AP) if Device hasVPN(VPN) where connect(VPN) = true.
+\end{lstlisting}
+Similarities between policies suggest that one could define a common schema of BYOD predicates, which would allow different policies to be compared \emph{precisely} using standard terms.
 
@@
 
+We have shown...
+
 \bibliographystyle{plain}
-\bibliography{paper}
+\begin{thebibliography}{1}
+\bibitem{Becker:2006vh}
+M.Y. Becker, C~Fournet, and A~D Gordon.
+\newblock {SecPAL: Design and semantics of a decentralized authorization language}.
+\newblock {\em Computer Security Foundations}, 2006.
+
+\bibitem{Guerin:2008we}
+N.R.C. Gu{\'e}rin.
+\newblock {Security Policy for the use of handheld devices in corporate environments},
+\newblock {\em SANS}.%, 2008.
+
+\bibitem{Hallett:2016vu}
+J. Hallett and D. Aspinall.
+\newblock {AppPAL for Android}.
+\newblock {\em Engineeering Secure Software and Systems}, 2016.
+
+\bibitem{Kennington:2014tr}
+G. Kennington, et~al.
+\newblock {Mobile Devices Policy},
+\newblock {\em Torbay and Southern Devon Health Care NHS Trust}.%, 2014.
+
+\bibitem{Williamson:2015tr}
+D. Williamson, A. Grzybowski, and S. Graham.
+\newblock {BYOD Policy: Use of Personally Owned Devices for University Work},
+\newblock {\em University of Edinburgh}.%, 2015.
+\end{thebibliography}
 \end{document}

### 2016-03-09 paper.tex
some proselint issues

@@
 This can present a challenge for corporate IT departments:
-  they need to secure their networks and data but as they do not provide the employees with the devices they have limited control over what software runs and how the devices are configured.
-As a means of controlling the devices, IT departments have taken to publishing mobile device policies.
-Employees must agree to follow these policies if they want to use their personal devices in work.
-Often these policies are specified using natural language.
-This is problematic as it can create ambiguity in how the policy should be enforced, and in how the IT department can confirm that the policy was followed.
-There may be issues with \emph{completeness} and \emph{consistency} in these policies, which can lead to problems in enforcement.
+  they want to secure their networks but have limited control over the software and configuration of personal devices.
+To ensure compliance IT departments have taken to publishing mobile device policies.
+Employees must agree to follow these policies if they want to use their personal devices at work.
+These policies are often specified using natural language.
+This can create ambiguity in how the policy should be enforced, and in how the IT department can confirm that the policy was followed.
+There may be issues with \emph{completeness} and \emph{consistency} in these policies, which can lead to confusion and mistakes.
 
 Logics of authorization are languages designed to express rules about permissible actions.
-\emph{AppPAL}~\cite{Hallett:2016vu} is a language designed to express policies about which mobile apps to use and install.
-AppPAL is an instantiation of Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} and can express complex delegation relationships as well as make use of external programs and constraints such as static analysis tools, whilst being decidable and having formal semantics.
-We believe AppPAL can also be used to help specify BYOD policies. 
-We present in Section~\ref{sec:translation} excerpts from the translation into AppPAL of three BYOD policies: one from a security policy template from the SANS institute to aid companies in developing their own policies~\cite{Guerin:2008we}, another from an NHS hospital trust describing what their doctors may do with their phones and their role in the treatment of patients~\cite{Kennington:2014tr}, finally a simplistic policy used in practice from the University of Edinburgh~\cite{Williamson:2015tr}.
+\emph{AppPAL}~\cite{Hallett:2016vu} is a language that expresses policies about which mobile apps to use and install.
+AppPAL is an instantiation of Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh}.
+It can express delegation relationships and use external constraints.
+Like SecPAL it is decidable and has formal semantics.
+We believe AppPAL can be applied to specify BYOD policies. 
+We present excerpts from an AppPAL translation of three BYOD policies: 
+    one a security policy template from the SANS institute to aid companies in developing their own policies~\cite{Guerin:2008we}, 
+    another from an NHS hospital trust~\cite{Kennington:2014tr},
+    and a simplistic BYOD policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
 
-% TODO: We found that...
+% TODO: We found that
 
@@
 \end{lstlisting}
-The NHS policy makes a distinction between \emph{clinical} and \emph{non-clinical} apps with each requiring approval through a different group before final approval is given by the \emph{Integrated Governance Committee}.
+The NHS policy makes a distinction between \emph{clinical} and \emph{non-clinical} apps;
+    with each requiring approval through a different group before final approval is given by the \emph{Integrated Governance Committee}.
 These rules are only theoretical however as no group has ever approved an app.
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
-Apps for work usage must not be downloaded onto corporately issued mobile devices (even if approved on the NHS apps store) unless they have been approved through the following Trust channels: Clinical apps; at the time of writing there are no apps clinically approved by the Trust for use with patients / clients.
+Apps for work usage must not be downloaded onto corporately issued mobile devices (even if approved on the NHS apps store) unless they have been approved through the following Trust channels: 
+    Clinical apps;
+        at the time of writing there are no apps clinically approved by the Trust for use with patients / clients. 
         However, if a member of staff believes that there are clinical apps or other technologies that could benefit their patients / clients, this should be discussed with the clinical lead in the first instance and ratification should be sought via the Care and Clinical Policies Group.
         A clinical app should not be used if it has not been approved via this group. 
-Business apps; at the time of writing there are no business (i.e., non-clinical) apps approved by the Trust for use other than those preloaded onto the device at the point of issue.
+    Business apps; 
+        at the time of writing there are no business (i.e., non-clinical) apps approved by the Trust for use other than those preloaded onto the device at the point of issue. 
         However, if a member of staff believes that there are apps or other technologies that could benefit their non-clinical work, ratification of the app must be sought via the Management of Information Group (MIG).
@@
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
-For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
-It is illegal to do so.
+For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle. It is illegal to do so.
 Please refer to the most up-to-date information via the Highways Agency.
 For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
-It is illegal to do so.
-Please refer to the most up-to-date information via the Highways Agency.''}]
+It is illegal to do so. Please refer to the most up-to-date information via the Highways Agency.''}]
 'nhs-policy' says Device mustNotOperate 
@@
 Whereas the SANS policy requires the use of hands-free devices when in a car.
-\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Conducting telephone calls or utilizing handhelds while driving can be a safety hazard.
+\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``%
+Conducting telephone calls or utilizing handhelds while driving can be a safety hazard.
 Drivers should use handhelds in hand only while parked or out of the vehicle.
-If employees must use a handheld device while driving, ⟨Company⟩ requires the use of hands-free headset devices.''}]
+If employees must use a handheld device while driving, \emph{Company} requires the use of hands-free headset devices.''}]
 'sans-policy' says Device mustNotOperate 
@@
 Other similarities appear when looking at how devices connect to networks.
-The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks, where as SANS says its okay if the access point is secured properly or a VPN is used:
+The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks; where as SANS says its okay if the access point is secured properly or a VPN is used:
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
@@
 
-\section{Conclusions}
+\section{Conclusions, Future and Related Work}
 % Related work:
@@
 
-We have shown...
+% TODO:
 

### 2016-03-09 paper.tex
first draft

@@
 
-\newcommand{\dotdotdot}[1]{$\[\cdots\]$}
+\newcommand{\dotdotdot}[1]{$[\cdots]$}
 
@@
   % State problem
-  Corporate BYOD policies are imprecisely specified using natural language.
+  BYOD policies are imprecisely specified using natural language.
   % Why is it interesting
-  This creates ambiguity and makes detecting issues, and comparing policies harder.
+  This creates ambiguity, may hide specification problems and make comparison harder.
   % What does my solution achieve
-  We show how AppPAL (an authorization logic for mobile app installation policies) can describe BYOD policies formally.
+  We show how AppPAL (an authorization logic) can be used to formalise BYOD policies.
   % What follows from solution
-  This suggests that BYOD policies can be enforced automatically, and with greater precision, than by relying on users.
+  This suggests that the policies could be enforced automatically with greater precision than by relying on users.
 \end{abstract}
@@
 
-Employees are increasingly bringing their own devices into their workplaces.
-This can present a challenge for corporate IT departments:
-  they want to secure their networks but have limited control over the software and configuration of personal devices.
-To ensure compliance IT departments have taken to publishing mobile device policies.
-Employees must agree to follow these policies if they want to use their personal devices at work.
-These policies are often specified using natural language.
-This can create ambiguity in how the policy should be enforced, and in how the IT department can confirm that the policy was followed.
-There may be issues with \emph{completeness} and \emph{consistency} in these policies, which can lead to confusion and mistakes.
+Employees bring their personal devices to work.
+This is a challenge for corporate IT departments:
+  they want to secure their networks but have limited control over a personal device's software and configuration.
+To ensure compliance IT departments publish mobile device policies.
+Employees must agree to follow them if they want to use their personal devices at work.
+Many policies are specified using natural language which may be ambiguous and hard to check for compliance.
 
-Logics of authorization are languages designed to express rules about permissible actions.
-\emph{AppPAL}~\cite{Hallett:2016vu} is a language that expresses policies about which mobile apps to use and install.
-AppPAL is an instantiation of Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh}.
-It can express delegation relationships and use external constraints.
-Like SecPAL it is decidable and has formal semantics.
-We believe AppPAL can be applied to specify BYOD policies. 
+Logics of authorization are languages to express what actions are permissible.
+Amongst other applicaitons they have been used in access control~\cite{Abadi:2003kta}, and to identify problems in electronic health records~\cite{Becker:2004fi}.
+\emph{AppPAL}~\cite{Hallett:2016vu} is an instantiation of Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} language that expresses mobile app installation policies.
+It makes use of delegation relationships and uses external constraints to formalise policies.
+
 We present excerpts from an AppPAL translation of three BYOD policies: 
-    one a security policy template from the SANS institute to aid companies in developing their own policies~\cite{Guerin:2008we}, 
-    another from an NHS hospital trust~\cite{Kennington:2014tr},
-    and a simplistic BYOD policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
-
-% TODO: We found that
+    one a security policy from the SANS institute to aid companies in developing their own rules~\cite{Guerin:2008we}, 
+    one from an NHS hospital trust~\cite{Kennington:2014tr},
+    and a BYOD policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
+We show how AppPAL can specifiy BYOD policies making them precise, identifying problems and aiding comparison.
 
@@
 
-It is common to find rules in policies describing what apps can be used on devices.
-This is modeled in AppPAL through the \texttt{isInstallable} predicate.
-The Edinburgh policy only recommends that apps come from a reputable source though what it means to be \emph{reputable} is left undefined. 
+Many BYOD policies describe what apps are usable at work.
+The Edinburgh policy recommends that apps come from a reputable source (though what it means to be \emph{reputable} is left undefined). 
+The SANS policy uses white and black lists of apps written by the IT department, however, the rule is repeated later in their document by another equivalent rule.
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Only download applications (‘apps’) or other software from reputable sources.''}]
@@
 \end{lstlisting}
-Whereas the SANS policy require the IT department maintain white and black lists of acceptable apps:
 \begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorzed applications and makes them available to users on the intranet.''}]
@@
 \end{lstlisting}
-This rule is replicated later in the policy by another recommendation that says the same:
 \begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``Only approved third party applications can be
@@
 The NHS policy makes a distinction between \emph{clinical} and \emph{non-clinical} apps;
-    with each requiring approval through a different group before final approval is given by the \emph{Integrated Governance Committee}.
-These rules are only theoretical however as no group has ever approved an app.
+    with each requiring approval through a different group before final approval is given by a commitee.
+In practice these rules are irrelevant, however, as no group has ever approved an app.
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
@@
         at the time of writing there are no apps clinically approved by the Trust for use with patients / clients. 
-        However, if a member of staff believes that there are clinical apps or other technologies that could benefit their patients / clients, this should be discussed with the clinical lead in the first instance and ratification should be sought via the Care and Clinical Policies Group.
-        A clinical app should not be used if it has not been approved via this group. 
+        However, if a member of staff believes that there are clinical apps \dotdotdot{or other technologies that could benefit their patients / clients, this should be discussed with the clinical lead in the first instance and} ratification should be sought via the Care and Clinical Policies Group.
+        \dotdotdot{A clinical app should not be used if it has not been approved via this group.}
     Business apps; 
         at the time of writing there are no business (i.e., non-clinical) apps approved by the Trust for use other than those preloaded onto the device at the point of issue. 
-        However, if a member of staff believes that there are apps or other technologies that could benefit their non-clinical work, ratification of the app must be sought via the Management of Information Group (MIG).
-        An app should not be used if it has not been approved via this group.
+        However, if a member of staff believes that there are apps \dotdotdot{or other technologies that could benefit their non-clinical work,} ratification of the app must be sought via the Management of Information Group (MIG).
+        \dotdotdot{An app should not be used if it has not been approved via this group.}
 Following approval through Care and Clinical Policies and / or MIG, final approval will be required through Integrated Governance Committee.''}]
@@
 
-In each case the rules for deciding whether an employee could install an app took the form of a delegation to one or more third-parties to approve apps.
-By translating the policies into AppPAL problems become immediately apparent: the Edinburgh policy is incomplete as there was no way to determine what stores were reputable, the SANS policy contains duplicated rules, and the NHS policy is redundant as no app had ever been approved for use.
+In all three policies delegation was used to decide whether an employee could install an app.
+By translating the policies into AppPAL problems become apparent: the Edinburgh policy is \emph{incomplete} as there was no way to determine what stores were reputable, the SANS policy \emph{contains duplicated rules}, and the NHS policy is \emph{redundant} as no app was ever been approved for use.
 In each case the AppPAL rule was no longer than the natural language policy, and in the case of the NHS policy considerably shorter and clearer.
 
-Some rules also appear to be common between different policies.
-For example both the NHS and SANS policies contain rules on the use of mobile devices in cars.
-The NHS policy requires employees do not use devices in cars, and recommends against using them even with hands-free equipment:
-\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
-For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle. It is illegal to do so.
-Please refer to the most up-to-date information via the Highways Agency.
-For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
-It is illegal to do so. Please refer to the most up-to-date information via the Highways Agency.''}]
-'nhs-policy' says Device mustNotOperate 
-  if Device isOwnedBy(Owner)
-  where inCar(Device) = true, isDriving(Owner) = true.
-\end{lstlisting}
-Whereas the SANS policy requires the use of hands-free devices when in a car.
+Some rules appear in different policies with minor changes.
+Both the NHS and SANS policies regulate the use of mobile devices in cars: by banning the use whilst driving.
+The SANS policy permits the use of hands-free devices, whereas the NHS policy recommends against them.
 \begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``%
@@
 If employees must use a handheld device while driving, \emph{Company} requires the use of hands-free headset devices.''}]
-'sans-policy' says Device mustNotOperate 
-  if Device isOwnedBy(Owner)
+'sans-policy' says Device mustNotOperate if Device isOwnedBy(Owner)
   where inCar(Device) = true, isDriving(Owner) = true, isUsingHandsFree(Device) = false.
 \end{lstlisting}
-The similarity between the two rules is immediately apparent when specified in AppPAL: the SANS version has an additional constraint but they are otherwise identical.
+\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
+For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
+\dotdotdot{It is illegal to do so. 
+Please refer to the most up-to-date information via the Highways Agency.}
+the Trust does not recommend using mobile devices in hands-free mode \dotdotdot{or with hands-free attachments} whilst driving.
+''}]
+'nhs-policy' says Device mustNotOperate if Device isOwnedBy(Owner)
+  where inCar(Device) = true, isDriving(Owner) = true.
+\end{lstlisting}
+When specified in AppPAL the similarities are immediately apparent: the SANS version has an additional constraint but they are otherwise identical.
+
 Other similarities appear when looking at how devices connect to networks.
-The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks; where as SANS says its okay if the access point is secured properly or a VPN is used:
+The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks (though again it does not specify what \emph{secure} actually means). 
+In contrast the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN as a last resort.
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
@@
 \end{lstlisting}
-Similarities between policies suggest that one could define a common schema of BYOD predicates, which would allow different policies to be compared \emph{precisely} using standard terms.
+By analysing the similarities in policies a framework of BYOD predicates could be defined that would allow policies to be compared \emph{precisely} using standard terms.
 
-\section{Conclusions, Future and Related Work}
+AppPAL can describe complex scenarios in policies.
+The NHS policy describes when a clinician can use their phone's camera as part of patient care.
+The rules require obtaining consent (delegation to the patient) as well as clinical approval (delegation to the clinician). 
+As well as helping clarify the policy, the AppPAL rules can aid with compliance:
+    a proof the AppPAL policy was satisfied might act as evidence that proper procedure was followed.
+\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
+Some mobile devices have the ability to take photographs / videos. 
+This function should not be used for photographs / videos of an individual’s care and treatment unless the device has encryption enabled and it is clinically appropriate to do so.
+If the photography / video facility is used as part of the recording of an individual’s care and treatment, the device user must ensure that the consent of the individual has been collected prior to taking any photograph / video.
+\dotdotdot{The individual needs to fully understand why the photograph / video is being taken and the member of staff plans to do with it, in particular if it will be shared. }
+A record of the consent must be entered into the individual’s care record. 
+''}]
+'nhs-policy' says Device canPhotograph(Patient) if Device isEncrypted, Patient canBePhotographed.
+'nhs-policy' says 'clinician' can-say Patient canBePhotographed
+  if Patient hasClinicalNeedForPhotograph, Patient hasConsentedToPhotograph
+  where recordedICRConsentForPhotograph(Patient) = true.
+'nhs-policy' says 'clinician' can-say Patient hasClinicalNeedForPhotograph.
+'nhs-policy' says Patient can-say Patient hasConsentedToPhotograph if Patient canConsent.
+\end{lstlisting}
+
+\section{Conclusions and Future Work}
 % Related work:
@@
 
-% TODO:
+We have shown that natural language BYOD policies contain ambiguities and mistakes.
+We have also shown how an authorization language, such as AppPAL, might help improve the policies by removing ambiguity, aiding comparison, making delegation relationships explicit and demonstrating compliance.
+Future work will look in detail at the implementation of a BYOD policy using AppPAL, any problems identified, and the degree to which the policy can be enforced automatically.
+Automatically inferring when AppPAL policies are incomplete, inconsistent, or have issues with redundancy would help policy designers avoid problems.
 
@@
 \newblock {\em University of Edinburgh}.%, 2015.
+
+\bibitem{Abadi:2003kta}
+M. Abadi.
+\newblock {Logic in access control},
+\newblock {\em Logic in Computer Science}, 2003.
+
+\bibitem{Becker:2004fi}
+M.Y. Becker, and P. Sewell,
+\newblock {Cassandra: flexible trust management, applied to electronic health records},
+\newblock {\em Computer Security Foundations}, 2004.
 \end{thebibliography}

### 2016-03-10 paper.tex
language tool rules

@@
 The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks (though again it does not specify what \emph{secure} actually means). 
-In contrast the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN as a last resort.
+In contrast, the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN as a last resort.
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
@@
 M. Abadi.
-\newblock {Logic in access control},
+\`newblock {Logic in access control},
 \newblock {\em Logic in Computer Science}, 2003.

### 2016-03-10 paper.tex
proselint

@@
 The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks (though again it does not specify what \emph{secure} actually means). 
-In contrast, the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN as a last resort.
+In contrast, the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN.
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]

### 2016-03-10 paper.tex
removing examples of passive voice

@@
   % What does my solution achieve
-  We show how AppPAL (an authorization logic) can be used to formalise BYOD policies.
+  We show how we can use AppPAL (an authorization logic) to formalise BYOD policies.
   % What follows from solution
-  This suggests that the policies could be enforced automatically with greater precision than by relying on users.
+  This suggests we can automatically enforce policies with fewer mistakes than by relying on users.
 \end{abstract}
@@
 Employees bring their personal devices to work.
-This is a challenge for corporate IT departments:
+Corporate IT departments can find this challenging:
   they want to secure their networks but have limited control over a personal device's software and configuration.
@@
 Employees must agree to follow them if they want to use their personal devices at work.
-Many policies are specified using natural language which may be ambiguous and hard to check for compliance.
+Policies specified using natural language can contain ambiguities.
+This makes compliance checking hard as automatic methods are hard to use with these policies.
 
-Logics of authorization are languages to express what actions are permissible.
-Amongst other applicaitons they have been used in access control~\cite{Abadi:2003kta}, and to identify problems in electronic health records~\cite{Becker:2004fi}.
-\emph{AppPAL}~\cite{Hallett:2016vu} is an instantiation of Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} language that expresses mobile app installation policies.
+Logics of authorization are languages used to express permissible actions.
+Their uses include access control~\cite{Abadi:2003kta}, and identifying problems in electronic health records~\cite{Becker:2004fi}, amongst other applications.
+\emph{AppPAL}~\cite{Hallett:2016vu} instantiates Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} language to express mobile app installation policies.
 It makes use of delegation relationships and uses external constraints to formalise policies.
+We believe it has applications to mobile device BYOD policies as well.
 
@@
 
-Many BYOD policies describe what apps are usable at work.
-The Edinburgh policy recommends that apps come from a reputable source (though what it means to be \emph{reputable} is left undefined). 
-The SANS policy uses white and black lists of apps written by the IT department, however, the rule is repeated later in their document by another equivalent rule.
+Many BYOD policies describe the apps usable in the workplace.
+The Edinburgh policy recommends apps come from reputable sources (though the meaning of \emph{reputable} is left undefined). 
+The SANS policy uses app black and white lists written by the IT department.
+Infact the SANS policy recommends this multiple times in their document.
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Only download applications (‘apps’) or other software from reputable sources.''}]
@@
 \end{lstlisting}
-\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorzed applications and makes them available to users on the intranet.''}]
+\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorized applications and makes them available to users on the intranet.''}]
 'sans-policy' says 'it-department' can-say App isInstallable.
@@
 \end{lstlisting}
-The NHS policy makes a distinction between \emph{clinical} and \emph{non-clinical} apps;
-    with each requiring approval through a different group before final approval is given by a commitee.
-In practice these rules are irrelevant, however, as no group has ever approved an app.
+The NHS policy distinguishes between \emph{clinical} and \emph{non-clinical} apps;
+    with both requiring approval through a different group before a committee gives final approval.
+In practice these rules are irrelevant: no group has ever approved an app.
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
@@
 
-In all three policies delegation was used to decide whether an employee could install an app.
-By translating the policies into AppPAL problems become apparent: the Edinburgh policy is \emph{incomplete} as there was no way to determine what stores were reputable, the SANS policy \emph{contains duplicated rules}, and the NHS policy is \emph{redundant} as no app was ever been approved for use.
-In each case the AppPAL rule was no longer than the natural language policy, and in the case of the NHS policy considerably shorter and clearer.
+All three policies use delegation to decide is an app is installable.
+By translating the policies into AppPAL problems become apparent: the Edinburgh policy is \emph{incomplete} as it lacks a means to determine what stores were reputable, the SANS policy \emph{contains duplicated rules}, and the NHS policy is \emph{redundant} as no app was ever approved for use.
+For all three policies the AppPAL rule is no longer than the natural language policy, and in the case of the NHS policy considerably shorter and clearer.
 
@@
 The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks (though again it does not specify what \emph{secure} actually means). 
-In contrast, the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN.
+In contrast, the SANS policy says what security features are required and that, whilst secure access points are preferred, an open access point is acceptable if used with a VPN.
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
@@
 As well as helping clarify the policy, the AppPAL rules can aid with compliance:
-    a proof the AppPAL policy was satisfied might act as evidence that proper procedure was followed.
+    a proof an AppPAL policy was satisfied might act as evidence that proper procedure was followed.
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
@@
 Future work will look in detail at the implementation of a BYOD policy using AppPAL, any problems identified, and the degree to which the policy can be enforced automatically.
-Automatically inferring when AppPAL policies are incomplete, inconsistent, or have issues with redundancy would help policy designers avoid problems.
+Automatic inference of when an AppPAL policies is incomplete, inconsistent, or has issues with redundancy would help policy designers avoid problems.
 

### 2016-03-11 paper.tex
Fixed the title
rewriting conclusion. started incorporating davids changes

@@
 
-\title{Specifying BYOD Policies with Authorization Logic}
-\titlerunning{Specifying BYOD Policies with Authorization Logic}
+\title{Specifying BYOD Policies With Authorization Logic}
+\titlerunning{Specifying BYOD Policies With Authorization Logic}
 \author{
-  Joseph Hallett\inst{1}
+  Joseph Hallett%\inst{1}
   \and
-  David Aspinall\inst{1}
+  David Aspinall%\inst{1}
 }
@@
   % What does my solution achieve
-  We show how we can use AppPAL (an authorization logic) to formalise BYOD policies.
+  We show how we can use AppPAL (an authorization logic) to formalise three BYOD policies.
   % What follows from solution
-  This suggests we can automatically enforce policies with fewer mistakes than by relying on users.
+  We identify potential problems in all three policies.
+  This suggests authorization logic may help in policy specification and enforcement.
 \end{abstract}
@@
 It makes use of delegation relationships and uses external constraints to formalise policies.
+AppPAL policies define predicates which can affect application installation (isInstallable) or operation;
+ they may be enforced by application rewriting or a modified version of the mobile platform security manager.
 We believe it has applications to mobile device BYOD policies as well.
 
-We present excerpts from an AppPAL translation of three BYOD policies: 
-    one a security policy from the SANS institute to aid companies in developing their own rules~\cite{Guerin:2008we}, 
-    one from an NHS hospital trust~\cite{Kennington:2014tr},
-    and a BYOD policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
+We present excerpts from an AppPAL translation of three BYOD policies. 
+It is designed to be readable; we introduce the language alongside the BYOD example excerpts from:
+    a security policy from the SANS institute to aid companies in developing their own rules~\cite{Guerin:2008we}, 
+    an NHS hospital trust~\cite{Kennington:2014tr},
+    and a policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
 We show how AppPAL can specifiy BYOD policies making them precise, identifying problems and aiding comparison.
@@
 
-Some rules appear in different policies with minor changes.
-Both the NHS and SANS policies regulate the use of mobile devices in cars: by banning the use whilst driving.
-The SANS policy permits the use of hands-free devices, whereas the NHS policy recommends against them.
-\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``%
-Conducting telephone calls or utilizing handhelds while driving can be a safety hazard.
-Drivers should use handhelds in hand only while parked or out of the vehicle.
-If employees must use a handheld device while driving, \emph{Company} requires the use of hands-free headset devices.''}]
-'sans-policy' says Device mustNotOperate if Device isOwnedBy(Owner)
-  where inCar(Device) = true, isDriving(Owner) = true, isUsingHandsFree(Device) = false.
-\end{lstlisting}
-\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
-For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
-\dotdotdot{It is illegal to do so. 
-Please refer to the most up-to-date information via the Highways Agency.}
-the Trust does not recommend using mobile devices in hands-free mode \dotdotdot{or with hands-free attachments} whilst driving.
-''}]
-'nhs-policy' says Device mustNotOperate if Device isOwnedBy(Owner)
-  where inCar(Device) = true, isDriving(Owner) = true.
-\end{lstlisting}
-When specified in AppPAL the similarities are immediately apparent: the SANS version has an additional constraint but they are otherwise identical.
+%Some rules appear in different policies with minor changes.
+%Both the NHS and SANS policies regulate the use of mobile devices in cars: by banning the use whilst driving.
+%The SANS policy permits the use of hands-free devices, whereas the NHS policy recommends against them.
+%\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``%
+%Conducting telephone calls or utilizing handhelds while driving can be a safety hazard.
+%Drivers should use handhelds in hand only while parked or out of the vehicle.
+%If employees must use a handheld device while driving, \emph{Company} requires the use of hands-free headset devices.''}]
+%'sans-policy' says Device mustNotOperate if Device isOwnedBy(Owner)
+%  where inCar(Device) = true, isDriving(Owner) = true, isUsingHandsFree(Device) = false.
+%\end{lstlisting}
+%\begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
+%For safety reasons, Trust staff must not use a hand held mobile device whilst driving any vehicle.
+%\dotdotdot{It is illegal to do so. 
+%Please refer to the most up-to-date information via the Highways Agency.}
+%the Trust does not recommend using mobile devices in hands-free mode \dotdotdot{or with hands-free attachments} whilst driving.
+%''}]
+%'nhs-policy' says Device mustNotOperate if Device isOwnedBy(Owner)
+%  where inCar(Device) = true, isDriving(Owner) = true.
+%\end{lstlisting}
+%When specified in AppPAL the similarities are immediately apparent: the SANS version has an additional constraint but they are otherwise identical.
 
-Other similarities appear when looking at how devices connect to networks.
+Similarities appear when looking at how devices connect to networks.
 The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks (though again it does not specify what \emph{secure} actually means). 
@@
 
-\section{Conclusions and Future Work}
+\section{Current Status}
 % Related work:
@@
 
-We have shown that natural language BYOD policies contain ambiguities and mistakes.
-We have also shown how an authorization language, such as AppPAL, might help improve the policies by removing ambiguity, aiding comparison, making delegation relationships explicit and demonstrating compliance.
-Future work will look in detail at the implementation of a BYOD policy using AppPAL, any problems identified, and the degree to which the policy can be enforced automatically.
-Automatic inference of when an AppPAL policies is incomplete, inconsistent, or has issues with redundancy would help policy designers avoid problems.
+So far we have developed AppPAL policies describing each of the BYOD policies.
+We have developed tools to identify when AppPAL policies may be incomplete, and aim to extend this to inconsistency and redundancy checks in future work.
+For example, when checking the \emph{isInstallable} predicate in the NHS policy our completeness checker spots the missing statements from the groups, and that the \emph{isInstallable} rule is unsatisfiable.
+\begin{lstlisting}
+The following assertions are unsatisfiable:
+  'nhs-policy' says App.1 isInstallable if App.1 isUsable, App.1 isFinallyApproved.
+
+These decisions may be derivable but we lack statements from the delegated party:
+  (via 'mig') 'nhs-policy' says * isUsable
+  (via 'igc') 'nhs-policy' says * isFinallyApproved
+  (via 'cacpg') 'nhs-policy' says * isUsable
+\end{lstlisting}
+Since the policies we are translating are informal, we should also question the accuracy of our formalisation.
+Future work will look at developing a testing process as part of the requirements capture, and working with policy owners to check that rules AppPAL postulates as true match the author's intentions.
+
+In general, BYOD policies are at an early stage.
+As policies grow and become more intricate tools like AppPAL might help ensure they are well specified.
 

### 2016-03-11 paper.tex
last of davids edits and additional citaiton

@@
     with both requiring approval through a different group before a committee gives final approval.
-In practice these rules are irrelevant: no group has ever approved an app.
+In practice these rules are irrelevant: no group has ever approved an app: perhaps unsurprisingly since 82\% of Android medical apps have basic privacy concerns~\cite{Blenner:2016ja}.
+
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
@@
 \end{lstlisting}
-Since the policies we are translating are informal, we should also question the accuracy of our formalisation.
+Since the BYOD policies are informal we should question the accuracy of our formalisation.
 Future work will look at developing a testing process as part of the requirements capture, and working with policy owners to check that rules AppPAL postulates as true match the author's intentions.
-
 In general, BYOD policies are at an early stage.
@@
 M. Abadi.
-\`newblock {Logic in access control},
+\newblock {Logic in access control},
 \newblock {\em Logic in Computer Science}, 2003.
+
+\bibitem{Blenner:2016ja}
+S.R. Blenner, et~al.
+\newblock {Privacy Policies of Android Diabetes Apps and Sharing of Health Information}
+\newblock {\em Journal of the American Medical Association}, 2016.
 

### 2016-03-11 paper.tex
spelling mistakes

@@
 
-\title{Specifying BYOD Policies With Authorization Logic}
-\titlerunning{Specifying BYOD Policies With Authorization Logic}
+\title{Specifying BYOD Policies With Authorisation Logic}
+\titlerunning{Specifying BYOD Policies With Authorisation Logic}
 \author{
@@
   % What does my solution achieve
-  We show how we can use AppPAL (an authorization logic) to formalise three BYOD policies.
+  We show how we can use AppPAL (an authorisation logic) to formalise three BYOD policies.
   % What follows from solution
   We identify potential problems in all three policies.
-  This suggests authorization logic may help in policy specification and enforcement.
+  This suggests authorisation logic may help in policy specification and enforcement.
 \end{abstract}
@@
 
-Logics of authorization are languages used to express permissible actions.
+Logics of authorisation are languages used to express permissible actions.
 Their uses include access control~\cite{Abadi:2003kta}, and identifying problems in electronic health records~\cite{Becker:2004fi}, amongst other applications.
@@
     and a policy used at The University of Edinburgh~\cite{Williamson:2015tr}.
-We show how AppPAL can specifiy BYOD policies making them precise, identifying problems and aiding comparison.
+We show how AppPAL can specify BYOD policies making them precise, identifying problems and aiding comparison.
 
@@
 The SANS policy uses app black and white lists written by the IT department.
-Infact the SANS policy recommends this multiple times in their document.
+In fact the SANS policy recommends this multiple times in their document.
 \begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Only download applications (‘apps’) or other software from reputable sources.''}]
@@
 \end{lstlisting}
-\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorized applications and makes them available to users on the intranet.''}]
+\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``The IT Department maintains a list of allowed and unauthorised applications and makes them available to users on the intranet.''}]
 'sans-policy' says 'it-department' can-say App isInstallable.

### 2016-03-11 paper.tex
printed edit

@@
   % Why is it interesting
-  This creates ambiguity, may hide specification problems and make comparison harder.
+  This creates ambiguity, may hide specification problems, and makes comparison harder.
   % What does my solution achieve
@@
 Logics of authorisation are languages used to express permissible actions.
-Their uses include access control~\cite{Abadi:2003kta}, and identifying problems in electronic health records~\cite{Becker:2004fi}, amongst other applications.
+Their uses include access control~\cite{Abadi:2003kta}, and identifying problems in electronic health records~\cite{Becker:2004fi} amongst other applications.
 \emph{AppPAL}~\cite{Hallett:2016vu} instantiates Becker~et~al{.}'s SecPAL~\cite{Becker:2006vh} language to express mobile app installation policies.
 It makes use of delegation relationships and uses external constraints to formalise policies.
-AppPAL policies define predicates which can affect application installation (isInstallable) or operation;
+AppPAL policies define predicates which can affect application installation (\emph{isInstallable}) or operation;
  they may be enforced by application rewriting or a modified version of the mobile platform security manager.
-We believe it has applications to mobile device BYOD policies as well.
+We believe AppPAL has applications to mobile device BYOD policies as well.
 
-We present excerpts from an AppPAL translation of three BYOD policies. 
-It is designed to be readable; we introduce the language alongside the BYOD example excerpts from:
+%We present excerpts from an AppPAL translation of three BYOD policies. 
+AppPAL is designed to be readable; we introduce the language alongside example excerpts from three BYOD including:
     a security policy from the SANS institute to aid companies in developing their own rules~\cite{Guerin:2008we}, 
@@
 The Edinburgh policy recommends apps come from reputable sources (though the meaning of \emph{reputable} is left undefined). 
-The SANS policy uses app black and white lists written by the IT department.
+%The SANS policy uses app black and white lists written by the IT department.
+The SANS policy encourages the IT department to maintain black-lists and white-lists.
 In fact the SANS policy recommends this multiple times in their document.
@@
     with both requiring approval through a different group before a committee gives final approval.
-In practice these rules are irrelevant: no group has ever approved an app: perhaps unsurprisingly since 82\% of Android medical apps have basic privacy concerns~\cite{Blenner:2016ja}.
+In practice these rules are irrelevant: no group has ever approved an app. 
+This is, perhaps, unsurprising as 82\% of Android medical apps have basic privacy concerns~\cite{Blenner:2016ja}.
 
@@
 All three policies use delegation to decide is an app is installable.
-By translating the policies into AppPAL problems become apparent: the Edinburgh policy is \emph{incomplete} as it lacks a means to determine what stores were reputable, the SANS policy \emph{contains duplicated rules}, and the NHS policy is \emph{redundant} as no app was ever approved for use.
+By translating the policies into AppPAL problems become apparent: the Edinburgh policy is \emph{incomplete} as it lacks a means to determine what stores were reputable, the SANS policy \emph{contains duplicated rules}, and the NHS policy is incomplete and contains \emph{redundant statements} as no app has ever been approved for use.
 For all three policies the AppPAL rule is no longer than the natural language policy, and in the case of the NHS policy considerably shorter and clearer.
@@
 \end{lstlisting}
-By analysing the similarities in policies a framework of BYOD predicates could be defined that would allow policies to be compared \emph{precisely} using standard terms.
+By analysing the similarities in policies a framework of BYOD predicates could be defined that would allow policies to be compared using standard terms \emph{precisely}.
 
@@
 The rules require obtaining consent (delegation to the patient) as well as clinical approval (delegation to the clinician). 
-As well as helping clarify the policy, the AppPAL rules can aid with compliance:
-    a proof an AppPAL policy was satisfied might act as evidence that proper procedure was followed.
+As well as helping clarify the policy, the AppPAL rules can aid with compliance---a proof an AppPAL policy was satisfied might act as evidence that proper procedure was followed.
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
@@
 So far we have developed AppPAL policies describing each of the BYOD policies.
-We have developed tools to identify when AppPAL policies may be incomplete, and aim to extend this to inconsistency and redundancy checks in future work.
-For example, when checking the \emph{isInstallable} predicate in the NHS policy our completeness checker spots the missing statements from the groups, and that the \emph{isInstallable} rule is unsatisfiable.
+We have developed tools to identify when AppPAL policies may be incomplete, and aim to extend them to inconsistency and redundancy checks in future work.
+For example, when checking the \emph{isInstallable} predicate in the NHS policy our completeness checker spots the missing statements from the delegated to groups, and that the \emph{isInstallable} rule is unsatisfiable.
 \begin{lstlisting}
@@
 \end{lstlisting}
-Since the BYOD policies are informal we should question the accuracy of our formalisation.
+As the BYOD policies are informal we should question the accuracy of our formalisation.
 Future work will look at developing a testing process as part of the requirements capture, and working with policy owners to check that rules AppPAL postulates as true match the author's intentions.
 In general, BYOD policies are at an early stage.
-As policies grow and become more intricate tools like AppPAL might help ensure they are well specified.
+As policies grow and become more intricate tools like AppPAL can help ensure they are well specified.
 

### 2016-03-11 paper.tex
submitted version

@@
   columns=flexible,
-  frame=single
+  frame=single,
+  framesep=0.5pt,
+  framexleftmargin=2.5pt,
+  framexrightmargin=2.5pt,
 }
@@
 In practice these rules are irrelevant: no group has ever approved an app. 
-This is, perhaps, unsurprising as 82\% of Android medical apps have basic privacy concerns~\cite{Blenner:2016ja}.
+This is, perhaps, unsurprising as 82\% of Android medical apps have basic privacy concerns~\cite{Blenner:2016ja,Knorr:2015st}.
 
@@
     Clinical apps;
-        at the time of writing there are no apps clinically approved by the Trust for use with patients / clients. 
-        However, if a member of staff believes that there are clinical apps \dotdotdot{or other technologies that could benefit their patients / clients, this should be discussed with the clinical lead in the first instance and} ratification should be sought via the Care and Clinical Policies Group.
+        at the time of writing there are no apps clinically approved by the Trust for use with patients/clients. 
+        However, if a member of staff believes that there are clinical apps \dotdotdot{or other technologies that could benefit their patients/clients, this should be discussed with the clinical lead in the first instance and} ratification should be sought via the Care and Clinical Policies Group.
         \dotdotdot{A clinical app should not be used if it has not been approved via this group.}
@@
         \dotdotdot{An app should not be used if it has not been approved via this group.}
-Following approval through Care and Clinical Policies and / or MIG, final approval will be required through Integrated Governance Committee.''}]
+Following approval through Care and Clinical Policies and/or MIG, final approval will be required through Integrated Governance Committee.''}]
 'nhs-policy' says App isInstallable if App isUsable, App isFinallyApproved.
@@
 \begin{lstlisting}[title={\footnotesize\textbf{NHS}:~\itshape ``%
-Some mobile devices have the ability to take photographs / videos. 
-This function should not be used for photographs / videos of an individual’s care and treatment unless the device has encryption enabled and it is clinically appropriate to do so.
-If the photography / video facility is used as part of the recording of an individual’s care and treatment, the device user must ensure that the consent of the individual has been collected prior to taking any photograph / video.
-\dotdotdot{The individual needs to fully understand why the photograph / video is being taken and the member of staff plans to do with it, in particular if it will be shared. }
-A record of the consent must be entered into the individual’s care record. 
-''}]
+Some mobile devices have the ability to take photographs/videos. 
+This function should not be used for photographs/videos of an individual’s care and treatment unless the device has encryption enabled and it is clinically appropriate to do so.
+If the photography/video facility is used as part of the recording of an individual’s care and treatment, the device user must ensure that the consent of the individual has been collected prior to taking any photograph/video.
+\dotdotdot{The individual needs to fully understand why the photograph/video is being taken and the member of staff plans to do with it, in particular if it will be shared. }
+A record of the consent must be entered into the individual’s care record.''}]
 'nhs-policy' says Device canPhotograph(Patient) if Device isEncrypted, Patient canBePhotographed.
@@
   'nhs-policy' says App.1 isInstallable if App.1 isUsable, App.1 isFinallyApproved.
-
 These decisions may be derivable but we lack statements from the delegated party:
@@
 As the BYOD policies are informal we should question the accuracy of our formalisation.
-Future work will look at developing a testing process as part of the requirements capture, and working with policy owners to check that rules AppPAL postulates as true match the author's intentions.
+Future work will look at developing a testing process as part of the requirements capture, and working with policy owners to check that rules AppPAL postulates as true indeed match the author's intentions.
 In general, BYOD policies are at an early stage.
-As policies grow and become more intricate tools like AppPAL can help ensure they are well specified.
+As policies grow and become more intricate, we believe that tools like AppPAL will help ensure they are well specified.
 
@@
 \newblock {\em Computer Security Foundations}, 2004.
+
+\bibitem{Knorr:2015st}
+K. Knorr, and D. Aspinall.
+\newblock {Security Testing for Android mHealth Apps}
+\newblock {\em Software Testing, Verification and Validation Workshops}, 2015.
 \end{thebibliography}
